Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-10 sections/correlated-sicm-and-fm.tex
minor

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Novak2013,Scheenen2015}
(Fig.~\ref{fig:sicm+fm}b--d). Furthermore, it has been used to first identify
primary cilia in a cell culture and subsequently use SICM to reveal whether
the selected cilium was extending into the extracellular space or was embedded
in the cell, an information which could not be retrieved by using FM alone
\cite{Zhou2018}.
% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

@@

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
  \caption{%
    \textbf{Two possible setups for a SSC microscope.}
    \textbf{a:} Diagram of the combined setup with a xyz sample scan.
    \textbf{b:} Diagram of the combined setup with a xy sample scan and a z probe and objective scan. 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sscm_setup}
\end{figure}

The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
dimensions (xyz) for imaging.

The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
all three dimensions, it is only moved in x and y directions, while probe and objective, controlled by
the same software, simultaneously move in z direction.

According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
same platform lead to cross-talk and consequentially artefacts in the SICM data.

Both setups keep the probe-objective distance constant and enable the acquisition of a fluorescence
image and a topography of the sample surface in the same scan. Photobleaching is equalized for every
point of the sample allowing quantitative analysis of the FM data.

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation allows not only for correlating
studies in fixed samples, but also studies of dynamics in live samples.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
  \caption{%
    \textbf{Combining SICM and SCM.}
    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
    VLPs adsorbed to the surface of COS 7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
    	\textit{Left:} Cell surface topography. 
    	\textit{Middle:} Fluorescence recording of the cell shown left. 
    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
    Reprinted with permission from ref \cite{Shevchuk2008}.
    \textbf{d:} Live COS 7 cells sequentially scanned by SSCM. Overlays of simmultaneously obtained 
    topographic and fluorescence scans. Fluorescence imaging was started 2 h 17 min after the first 
    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2 h 40 min. 
    Reprinted with permission from ref \cite{Gorelik2002}.
  }
  \label{fig:sicm+scm}
\end{figure}

>>>>

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Novak2013,Scheenen2015}
(Fig.~\ref{fig:sicm+fm}b--d). Furthermore, it has been used to first identify
primary cilia in a cell culture and subsequently use SICM to reveal whether
the selected cilium was extending into the extracellular space or was embedded
in the cell, an information which could not be retrieved by using FM alone
\cite{Zhou2018}.

% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

@@

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
\begin{figure}
%  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
  \caption{%
    \textbf{Two possible setups for a combined SIC and SSC microscope.}
    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sicm+sscm_setup}
\end{figure}
